Pteropod physiological analysis

### 2018-03-12 physio.Rmd
fixed issue with na.omit in physio

Pairs plot
```{r, fig.height = 8, fig.width = 8}
dat <- ptedat %>% 
  select(one_of('CTD', ptechr)) %>% 
  na.omit %>% 
  inner_join(envdat, by = 'CTD') %>% 
  select(one_of(c('CTD', envchr, ptechr)))

@@

env <- select(dat_frm, one_of(envchr)) %>% 
  decostand(method = 'range')
pte <- select(dat_frm, one_of(ptechr)) %>% 
  decostand(method = 'range')

>>>>

Pairs plot
```{r, fig.height = 8, fig.width = 8}
dat <- ptedat %>% 
  select(one_of('CTD', ptechr)) %>% 
  left_join(envdat, by = 'CTD') %>% 
  select(one_of(c('CTD', envchr, ptechr)))

@@

env <- dat_frm %>% 
  na.omit %>% 
  select(., one_of(envchr)) %>% 
  decostand(method = 'range')
pte <- dat_frm %>% 
  na.omit %>% 
  select(one_of(ptechr)) %>% 
  decostand(method = 'range')
